Language-Based Security for Low-Level MPC

### 2024-09-02 ppdp24/slides.tex
checkpoint

@@

>>>>

\section{Compositional Properties of Circuits}

@@

  \begin{exampleblock}{2-Party GMW}
    Rep.~invariant: each client in $\setit{1,2}$ holds a share of wire values.
    \begin{itemize}
    \item $\ttt{andgmw}(x,y,z)$:
      \begin{itemize}
      \item Input shares $\mx{x}{1}$, $\mx{x}{2}$ and $\mx{y}{1}$, $\mx{y}{2}$--
        wire value for $x$ is $\mx{x}{1} + \mx{x}{2}$, etc.
      \item Output shares $\mx{z}{1}$, $\mx{z}{2}$ received during gate execution.
      \end{itemize}
    \end{itemize}

  \end{exampleblock}

\begin{frame}

  \begin{exampleblock}{2-Party GMW (Contd.)}
    \begin{itemize}
    \item $\ttt{andgmw}(x,y,z)$:
      \begin{itemize}
      \item Picking dummy for $x,y,z$, we can automatically generate a
        pmf under all possible wire inputs.
      \item Pmf can be queried to verify critical properties-- e.g., the
        uniform distribution of output shares under any input conditions. 
      \end{itemize}
      Once properties of gates are verified, we can show that rep.~invariants
      are maintained in any circuit.
    \end{itemize}

  \end{exampleblock}
